\documentclass[12pt]{article}

\usepackage[colorlinks=true, urlcolor={blue}, citecolor={black}, linkcolor={blue}]{hyperref}
\usepackage{url}

%% Choose font system: https://github.com/heathermiller/healy-article/blob/master/healy-article.tex
\usepackage{fontspec} % comment out if not using xelatex
\usepackage{xunicode} % comment out if not using xelatex
\setromanfont[Mapping=tex-text,Numbers=OldStyle,BoldFont={Minion Pro Bold}]{Minion Pro}
\setsansfont[Mapping=tex-text]{Minion Pro}
% \setmonofont[Mapping=tex-text,Scale=MatchLowercase]{PragmataPro}
\setmonofont[Mapping=tex-text,Scale=MatchLowercase,BoldFont={Consolas Bold}]{Consolas}

% Spacing
\usepackage{setspace}

% Margins
\usepackage[margin = 1in]{geometry}

% tikz
\usepackage{tikz}

% Header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Gannon and Kent \thepage}
\fancypagestyle{firststyle}
{
	\fancyhf{} 
	\fancyfoot[C]{Page \thepage}
}

% For table
\usepackage[table,xcdraw]{xcolor}
\usepackage{multirow}

% Bibiliography
\usepackage[round]{natbib}

%=======%
% Title %
%=======%
% Note: \vspace for raising title to save space
\title{%\vspace{-1.75cm}
Arms Sharing in Conflict Theaters}
\author{
	J. Andres Gannon\footnote{\texttt{jagannon@ucsd.edu}}
	\and 
	Daniel Kent\footnote{\texttt{kent.249@osu.edu}}}


\begin{document}

\maketitle

% 250 word limit for polnet proposal
% Polnet funding requires: 500 word statement (copy and pasted) and letter of
% rec by feb 1.

% Opening
What determines the magnitude of alliance contributions to conflict theaters?
At the outbreak of the 1990 Persian Gulf War, the French military's
budget was approximately double that of their Italian counterpart -- 58,149 and
30,768 million 2015 U.S. dollars,
respectively.\footnote{\url{https://www.sipri.org/sites/default/files/Milex-constant-2015-USD.pdf}}
However, in troops alone, France contributed over ten times as many
forces to the conflict as Italy -- 20,000 as opposed to 1,900 military
personnel. Though the Italian forces were not without value, their relative
size demonstrates a simple but important point: not all alliance
commitments are created equal.
% Why important
%Indeed, alliances are particularly consequential when their commitments are
%differentiable from cheap talk.
Indeed, if an ally is not expected to provide resources
to a conflict in proportion with its capabilities, then the alliance
itself is of far less consequence than it would otherwise be.
% Related but insufficient literature
Yet, empirical investigations of alliances and conflict processes tend
to avoid this distinction, instead focusing on: the formation of
alliances, how alliances influence the initiation of disputes, or how
alliances link to issues beyond the use of military force.
% Our contribution
We shed light on this important topic by developing a
theoretical framework for and conducting an empirical investigation of
the determinants of alliance contributions to conflict theaters.
Through a new data set of country-level military portfolios and
contributions to conflicts, we measure the type of technologies and
amount of forces that states have deployed in conflict theaters since the
end of the Cold War (which?).% IISS has "forces abroad" option for each country-year.
We then apply techniques for statistical inference in social networks to produce
insights into the strategic considerations that influence decisions to
provide various military capabilities to ongoing conflicts.
% Payoff
This project (something about how it will help the lit and is
relevant to current debates about alliance reliability amidst various
stresses to the international order -- NATO, North Korea, China.)




%\textbf{Rambling:} Countries don't want to spend too much (coordination problem where
%everyone wants the other state to provide the expensive guns), but
%benefit from a succesful conflict effort. Much like alleyway scenario
%where everyone wants cops called, but only for one person to call the
%cops. Similarly, everyone wants to the war effort to
%succeed, but nobody wants to provide the expensive guns. Or everyone
%wants to provide a unique tek, but for this tek to be cheap for them. So there is a
%coordination problem in reaching equilibrium of each state providing a
%single type of tek, but for that to be the least expensive tek possible.

%\bibliographystyle{apa}
%\bibliography{} 

\end{document}