---
title: "02a_Cleaning_DV"
author: "J Andres Gannon"
date: "August 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load and clean
Load the RData files containing the spreadsheets for the IISS deployment to Afghanistan data and country-year troop levels
```{r}
iiss_deployment <- readRDS(file = paste0(here::here(), '/data/iiss_deployment.rds'))
iiss_troops <- readRDS(file = paste0(here::here(), '/data/iiss_troops.rds'))
```

The country-years in both datasets refer to the IISS publication year which is one year prior to the actual calendar year the data describes
```{r}
iiss_deployment$year <- iiss_deployment$year - 1
iiss_troops$year <- iiss_troops$year - 1
```

Narrow the datasets to just the years 2001-2014, the scope of the Afghanistan war
```{r}
# Subset deployment data

# Subset troop data

```

# Merge
Merge the two datasets into a single dataframe
```{r}
iiss_afghan <-
```

# Create new ratio values
```{r}

```

# Save final dataset
```{r}
saveRDS(iiss_afghan, paste0(here::here(),"/data/","iiss_afghan.rds"))
```
